---
title: "ANLY 503 Exam"
author: "Yuqi Wang"
date: "November 23, 2018"
output: html_document
---
## Three plots with ggplot2

### Read in data

```{r}
hr_data <- read.csv('Human Resources Data Set/HRDataset_v9.csv') 
hr_data$Pay.Rate.Level <- as.factor(as.numeric(cut(hr_data$Pay.Rate, 6)))

options(scipen=999)  # turn-off scientific notation like 1e+48
#remove.packages(c("ggplot2", "data.table"))
#install.packages('Rcpp', dependencies = TRUE)
#install.packages('ggplot2', dependencies = TRUE)
#install.packages('data.table', dependencies = TRUE)
library(ggplot2)
```

### ggplot (Pay.Rate vs Sex)

```{r fig1, fig.width = 10, fig.asp = .62}
theme_set(theme_classic())

# Histogram on a Continuous (Numeric) Variable
g <- ggplot(hr_data, aes(Pay.Rate)) + scale_fill_brewer(palette = "Spectral")

g + geom_histogram(aes(fill=Sex), 
                   binwidth = 2, 
                   col="black", 
                   size=.1) +  # change binwidth
  labs(title="Pay Rate Histogram", 
       subtitle="Pay Rate across two Genders")  

ggsave('payrate_hist.jpg', width = 10, height = 6.2)
```



```{r fig2, fig.width = 10, fig.asp = .62}

theme_set(theme_bw())

# Scatterplot
gg <- ggplot(hr_data, aes(x=Days.Employed, y=Pay.Rate)) + 
  geom_point(aes(col=Sex)) + 
  geom_smooth(method="loess", se=F) + 
  #xlim(c(18, 75)) + 
  ylim(c(10, 90)) + 
  labs(subtitle="Pay Rate vs Days Employed", 
       y="Pay Rate", 
       x="Days Employed", 
       title="Scatterplot", 
       caption = "Source: HR dataset")

plot(gg)
ggsave('payrate_scatter.jpg', width = 10, height = 6.2)

```




```{r fig3, fig.width = 10, fig.asp = .62}

# plot
g <- ggplot(hr_data, aes(RaceDesc, Pay.Rate))
g + geom_boxplot() + 
  geom_dotplot(binaxis='y', 
               stackdir='center', 
               dotsize = .5, 
               fill="red") +
  facet_wrap(~ Sex, nrow=1) +
  theme(axis.text.x = element_text(angle=45, vjust=0.6)) + 
  labs(title="Box plot + Dot plot", 
       subtitle="Pay Rate vs Race: Each dot represents 1 row in source data",
       caption="Source: HR dataset",
       x="Race",
       y="Pay Rate")
  #theme_gray()

ggsave('payrate_boxplot.jpg', width = 10, height = 6.2)
```

### networkD3


```{r}

library(networkD3)

edgeList <- subset(hr_data, select=c("Performance.Score","Pay.Rate"))
colnames(edgeList) <- c("Source", "Target")

nodeList <- subset(hr_data, select=c("Pay.Rate", "Pay.Rate.Level"))
colnames(nodeList) <- c("nodeBetweenness", "nodeDegree")
nodeList['nName'] <- hr_data$Pay.Rate
(head(nodeList))


D3_network <- simpleNetwork(edgeList, Source = 1, Target = 2, height = NULL, width = NULL,
  linkDistance = 90, charge = -50, fontSize = 15, fontFamily = "serif",
  linkColour = "#666", nodeColour = "#3182bd", opacity = 0.6, zoom = T)

# Plot network
D3_network 



# Save network as html file
saveNetwork(D3_network, "D3network.html", selfcontained = TRUE)

```


D3_network <- forceNetwork(Links = edgeList, # data frame that contains info about edges
                           Nodes = nodeList, # data frame that contains info about nodes
                           Source = "Source", # ID of source node 
                           Target = "Target", # ID of target node
                           #Value = "Weight", # value from the edge list (data frame) that will be used to value/weight relationship amongst nodes
                           NodeID = "nName", # value from the node list (data frame) that contains node description we want to use (e.g., node name)
                           Nodesize = "nodeBetweenness",  # value from the node list (data frame) that contains value we want to use for a node size
                           Group = "nodeDegree",  # value from the node list (data frame) that contains value we want to use for node color
                           #height = 500, # Size of the plot (vertical)
                           #width = 1000,  # Size of the plot (horizontal)
                           #fontSize = 20, # Font size
                           #linkDistance = networkD3::JS("function(d) { return 10*d.value; }"), # Function to determine distance between any two nodes, uses variables already defined in forceNetwork function (not variables from a data frame)
                           #linkWidth = networkD3::JS("function(d) { return d.value/5; }"),# Function to determine link/edge thickness, uses variables already defined in forceNetwork function (not variables from a data frame)
                           #opacity = 0.65, # opacity
                           zoom = TRUE) # ability to zoom when click on the node
                           #opacityNoHover = 0.1) # edge colors



D3_network 

saveNetwork(D3_network, "D3network.html", selfcontained = TRUE)


### Leaflet

```{r}
#install.packages("tigris")
#install.packages("dplyr")
#install.packages("leaflet")

library(tigris)
library(dplyr)
library(leaflet)
library(rgdal)

# Downloading the shapefiles for states at the lowest resolution
states <- states(cb=T)

state_unemp <- read.csv("Unemployment by state.csv", stringsAsFactors = F)
state_unemp$X2016 <- state_unemp$X2016*100
state_unemp$X2015 <- state_unemp$X2015*100
state_unemp$X2014 <- state_unemp$X2014*100

###############################################
# Now we use the Tigris function geo_join to bring together 
# the states shapefile and the sb_states dataframe -- STUSPS and state 
# are the two columns they'll be joined by

states_merged_sb <- geo_join(states, state_unemp, "STUSPS", "State_abbr")
#hr_map <- aggregate(Pay.Rate~State, data = hr_data, FUN = mean)
#i <- sapply(hr_map, is.factor)
#hr_map[i] <- lapply(hr_map[i], as.character)
#write.csv(hr_map, file = "hr_map.csv")

hr_map <- read.csv("hr_map.csv", stringsAsFactors = F)

#hr_states <- geo_join(states, hr_map, "STUSPS", "State")

# Creating a color palette based on the number range in the total column
pal <- colorNumeric("Greens", domain=c(0,10))


# Getting rid of rows with NA values
# Using the Base R method of filtering subset() because we're dealing with a SpatialPolygonsDataFrame and not a normal data frame, thus filter() wouldn't work

states_merged_sb <- subset(states_merged_sb, !is.na(X2016))
states_merged_sb <- subset(states_merged_sb, !is.na(X2015))
states_merged_sb <- subset(states_merged_sb, !is.na(X2014))

hr_states <- subset(hr_states, !is.na(Pay.Rate))

# Setting up the pop up text
popup_sb2016 <- paste0("Umemployment rate in 2016: ", as.character(states_merged_sb$X2016), "%")

popup_sb2015 <- paste0("Umemployment rate in 2015: ", as.character(states_merged_sb$X2015), "%")

popup_sb2014 <- paste0("Umemployment rate in 2014: ", as.character(states_merged_sb$X2014), "%")

popup_pay <- paste0("Average pay rate of employees of our company in State ", as.character(hr_map$State),": $", as.character(hr_map$Pay.Rate))

# Mapping it with the new tiles CartoDB.Positron
m <- leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  setView(-98.483330, 38.712046, zoom = 4) %>% 
  
  ### 2016
  addPolygons(data = states_merged_sb , 
              group = '2016',
              fillColor = ~pal(states_merged_sb$X2016), 
              fillOpacity = 0.7, 
              weight = 0.2, 
              smoothFactor = 0.2, 
              highlight = highlightOptions(
                  weight = 5,
                  color = "#666",
                  fillOpacity = 0.7),
              label=popup_sb2016,
              labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>%
  
  ### 2015
  addPolygons(data = states_merged_sb , 
              group = '2015',
              fillColor = ~pal(states_merged_sb$X2015), 
              fillOpacity = 0.7, 
              weight = 0.2, 
              smoothFactor = 0.2, 
              highlight = highlightOptions(
                  weight = 5,
                  color = "#666",
                  fillOpacity = 0.7),
              label=popup_sb2015,
              labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>%
  
  ### 2014
  addPolygons(data = states_merged_sb , 
              group = '2014',
              fillColor = ~pal(states_merged_sb$X2014), 
              fillOpacity = 0.7, 
              weight = 0.2, 
              smoothFactor = 0.2, 
              highlight = highlightOptions(
                  weight = 5,
                  color = "#666",
                  fillOpacity = 0.7),
              label=popup_sb2014,
              labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>%
  addLegend(pal = pal, 
            values = 0:10, 
            position = "bottomright", 
            title = "Unemployment Rate") %>% 
  
  ### add circle
  addMarkers(data = hr_map,
             lat=~lat, lng=~long,
             group = 'Average Payrate',
             #radius=~Pay.Rate ,
             label = popup_pay,
             labelOptions = labelOptions(noHide = F,opacity=0.9))


Groupnames <- c("2016", "2015", "2014")


m <- m %>%
  # Add layers controls
  addLayersControl(
    baseGroups = Groupnames,
    overlayGroups = c('Average Payrate'),
    options = layersControlOptions(collapsed = FALSE)
  )
  # Add common legend
  #addLegend(colors = c("#4367F4", "#FF0000"),
  #          labels = c("Zones d'avis", "Zones de TAC"),
  #          opacity = c(0.8, 0.5))


library(htmlwidgets)
saveWidget(m, file="leafletMap.html")

```


### 3d scatter plot

```{r}
#install.packages('threejs')
library(threejs)
library(htmlwidgets)
library(RColorBrewer)

MyJ3=scatterplot3js(hr_data$Age,hr_data$Pay.Rate, hr_data$Days.Employed,color = c("#377EB8", "#E41A1C","#33CC00")[as.factor(hr_data$CitizenDesc)],axisLabels=c("Age","Pay Rate","Days Employed"),size=0.5)

#Eligible NonCitizen       Non-Citizen       US Citizen

saveWidget(MyJ3, file="hr3D.html")

display.brewer.pal(n = 8, name = 'Set1')
brewer.pal(n = 8, name = "Set1")
```



### plotly

```{r}
#install.packages("htmlwidgets")
#install.packages("plotly")
install.packages("dplyr")

library(plotly)
library(datasets)
library(xml2)
library(htmlwidgets)
######Plotly MAP
##set API keys once
Sys.setenv("plotly_username"="yw545")
Sys.setenv("plotly_api_key"="4cLtBnFZAahayYzX5d8u")

df <- read.csv("average monthly recruitment resignation rate/average-monthly-recruitment-resignation-rate-by-broad-occupational-group.csv", stringsAsFactors = F)
df_quarter <- as.data.frame(table(df$quarter))
df_occ <- as.data.frame(table(df$occupation1))
x <- df_quarter$Var1
y1 <- df$recruitment_rate[df$occupation1 == df_occ$Var1[1]]
y2 <- df$recruitment_rate[df$occupation1 == df_occ$Var1[2]]
y3 <- df$recruitment_rate[df$occupation1 == df_occ$Var1[3]]

y21 <- df$resignation_rate[df$occupation1 == df_occ$Var1[1]]
y22 <- df$resignation_rate[df$occupation1 == df_occ$Var1[2]]
y23 <- df$resignation_rate[df$occupation1 == df_occ$Var1[3]]

data <- data.frame(x, y1, y2, y3)


# font style
f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "black")

# annotations
a <- list(
  text = "Clerical, sales and services workers",
  font = f,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

b <- list(
  text = "Production and transport operators, cleaners and labourers",
  font = f,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

c <- list(
  text = "Professional, managers, executive and technicians",
  font = f,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)


p1 <- plot_ly(data, x = ~x, y = ~y1, name = 'recruitment rate', type = 'scatter', mode = 'lines+markers') %>%
  add_trace(y = ~y21, name = 'resignation rate', mode = 'lines+markers')  %>%
  layout(annotations = a)

p2 <- plot_ly(data, x = ~x, y = ~y2, name = 'recruitment rate', type = 'scatter', mode = 'lines+markers') %>%
  add_trace(y = ~y22, name = 'resignation rate', mode = 'lines+markers')  %>%
  layout(annotations = b)

p3 <- plot_ly(data, x = ~x, y = ~y3, name = 'recruitment rate', type = 'scatter', mode = 'lines+markers') %>%
  add_trace(y = ~y23, name = 'resignation rate', mode = 'lines+markers')  %>%
  layout(annotations = c)

p <- subplot(p1, p2, p3, nrows = 3, shareX = TRUE)  %>%
  layout(showlegend = T)


# Create a shareable link to your chart
# Set up API credentials: https://plot.ly/r/getting-started
chart_link = api_create(p, filename="line-mode1")
chart_link


```


output: https://plot.ly/~yw545/33.embed

### wordcloud

```{r fig4, fig.width = 10, fig.asp = 1}

#install.packages("wordcloud") # word-cloud generator 
# Load
library(wordcloud)
library(RColorBrewer)

Position <- as.character(hr_data$Position)
d <- as.data.frame(table(Position))

set.seed(1234)
wordcloud(words = d$Position, freq = d$Freq, min.freq = 1,
          max.words=200, random.order=F,
          colors=brewer.pal(8, "Dark2"))

```



















